---
title: "Workshops and teaching"
format:
  html:
    toc: true
    toc-depth: 2 
---

```{=html}
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/6.0.0-beta3/css/all.min.css">
<div class="custom-sidebar">
  <div class="sidebar-icon" onclick="toggleSidebar()">☰</div>
  <div class="sidebar-content">
    <h3>Contact</h3>
    <p><i class="fas fa-envelope email-icon"></i> <a href="mailto:youremail@example.com">youremail@example.com</a></p>
    <p><i class="fas fa-phone-alt phone-icon"></i> Phone: (123) 456-7890</p>
    <p><i class="fab fa-linkedin linkedin-icon"></i> <a href="https://www.linkedin.com/in/yourprofile" target="_blank">yourprofile</a></p>
  </div>
</div>

```


<script>
  function toggleSidebar() {
    const sidebarContent = document.querySelector('.sidebar-content');
    sidebarContent.classList.toggle('visible');
  }
</script>


Lorem ipsum odor amet, consectetuer adipiscing elit. Quam nullam pretium malesuada potenti commodo rutrum molestie tincidunt sodales. Risus nulla dui faucibus odio est phasellus tempus. Sollicitudin dapibus nunc ex congue nostra sapien velit. Praesent pellentesque vitae sociosqu orci magnis habitant maximus metus quisque. Velit tempus ad sodales hac; suspendisse suscipit.

```{r}
#| echo: false
#| column: margin

knitr::kable(
  mtcars[1:3, 1:3]
)
```

Faucibus accumsan ipsum et tempor fringilla placerat nisl ultrices. Suscipit dignissim finibus platea efficitur inceptos consequat orci sem. Himenaeos adipiscing ultrices ex; rutrum dignissim turpis. Libero sociosqu lacinia nibh; potenti elit viverra. Senectus fames fringilla praesent nascetur lacus lobortis dui tortor. Felis ridiculus lorem senectus convallis conubia nec phasellus nisi. Potenti sodales rhoncus et penatibus auctor morbi erat augue iaculis. Egestas dictumst phasellus class nec facilisis sapien lectus maximus iaculis. Quam nascetur fusce vivamus proin dolor; magna tempus curae.

::: {.column-margin}

Hi! I'm a side note ........................................ ,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,,, !

:::

# Programming  

## Git {#git}

```{r}
#| child: "workshop/git.qmd"
```

## Plain text {#plaintext}

```{r}
#| child: "workshop/plaintext.qmd"
```

## API's {#api}

```{r}
#| child: "workshop/api.qmd"
```

# Methods

## Regression {#project1}

```{r}
#| child: "workshop/regression.qmd"
```

## Project 2 {#project2}

```{r}
#| child: "workshop/decomposition.qmd"
```



<!-- Right Margin Sidebar -->
<div class="contact-sidebar">
  <h3>Contact Me</h3>
  <p>Email: youremail@example.com</p>
  <p>Phone: (123) 456-7890</p>
  <p>LinkedIn: <a href="https://www.linkedin.com/in/yourprofile" target="_blank">yourprofile</a></p>
</div>



::: {.cell}

```{=html}
<style>
  /* Styling for all h1 (Part) headers with fold icons */
  main h1 {
    cursor: pointer;
    font-weight: bold;
    color: #333;
  }
  main h1::after {
    content: " ▼"; /* Adds an arrow icon for Parts */
  }
  main h1.collapsed::after {
    content: " ►"; /* Changes icon when Part is collapsed */
  }

  /* Styling for h2 (Section) headers under Parts */
  main h2 {
    cursor: pointer;
    font-weight: bold;
  }
  main h2::after {
    content: " ▼"; /* Adds an arrow icon for visibility */
  }
  main h2.collapsed::after {
    content: " ►"; /* Changes icon when section is collapsed */
  }
</style>

<script>
  document.addEventListener("DOMContentLoaded", function() {
    // Select all Part headers (h1) within the main content area
    const parts = document.querySelectorAll("main h1");

    parts.forEach((part, index) => {
      part.style.cursor = "pointer";

      // Collect all elements under this Part until the next h1
      let nextSibling = part.nextElementSibling;
      const partContent = [];

      while (nextSibling && nextSibling.tagName !== "H1") {
        partContent.push(nextSibling);
        nextSibling = nextSibling.nextElementSibling;
      }

      // If this is the first h1 header, show it expanded by default
      if (index === 0) {
        part.classList.add("expanded"); // Keeps the icon consistent
      } else {
        // Hide content initially for other h1 headers
        partContent.forEach(element => element.style.display = "none");
      }

      // Toggle visibility of the Part content on click
      part.addEventListener("click", () => {
        const isVisible = partContent[0].style.display === "block";
        partContent.forEach(element => {
          element.style.display = isVisible ? "none" : "block";
        });
        part.classList.toggle("collapsed", !isVisible);
      });
    });

    // Select all Section headers (h2) within the main content under each Part
    const sections = document.querySelectorAll("main h2");

    sections.forEach(section => {
      section.style.cursor = "pointer";

      // Collect all elements under this Section until the next h2 or h1
      let nextSibling = section.nextElementSibling;
      const sectionContent = [];

      while (nextSibling && nextSibling.tagName !== "H2" && nextSibling.tagName !== "H1") {
        sectionContent.push(nextSibling);
        nextSibling = nextSibling.nextElementSibling;
      }

      // Hide the Section content by default
      sectionContent.forEach(element => element.style.display = "none");

      // Toggle visibility of the Section content on click
      section.addEventListener("click", (event) => {
        event.stopPropagation(); // Prevents toggling the parent h1
        const isVisible = sectionContent[0].style.display === "block";
        sectionContent.forEach(element => {
          element.style.display = isVisible ? "none" : "block";
        });
        section.classList.toggle("collapsed", !isVisible);
      });
    });
  });
</script>

```
:::